Community Similarity Analysis

### 2022-10-03 scripts/workshop/comm_similarity.Rmd
update community similarity analysis rmd

---
title: "distances"
author: "Daniel Suh"
date: "2022-10-03"
output: html_document
---

@@

dist_df %<>% mutate(resid_sign = ifelse(resid>0,1,0))

dist_df %>% ggplot(.,aes(x=j_dist,y=p_dist,color=resid_sign)) + geom_point() + scale_color_viridis_b()
```

>>>>

---
title: "Community Similarity Analysis"
author: "Daniel Suh"
date: "2022-10-03"
output: html_document
---

@@

dist_df %<>% mutate(resid_sign = as.factor(ifelse(resid>0,1,0)))

dist_df %>% ggplot(.,aes(x=j_dist,y=p_dist,color=resid_sign)) + geom_point() + scale_color_viridis_d()
```
